Results

### 2025-08-27 notebooks/000_data.qmd
refactor: clean a bit

```{julia}
using Dates
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using SPEDAS: tplot, set_meta
using Speasy
using GLMakie
```

@@

```{julia}
tmin = DateTime("2021-01-15")
tvars = [
    "PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
    "PSP_SWP_SPI_SF00_L3_MOM/VEL_SC",
    "PSP_SWP_SPI_SF00_L3_MOM/VEL_INST",
    "PSP_SWP_SPI_SF00_L3_MOM/MAGF_SC",
    "PSP_FLD_L2_MAG_SC_4_SA_PER_CYC/psp_fld_l2_mag_SC_4_Sa_per_Cyc"
]
tplot(tvars, tmin, tmin + Hour(1))
```

@@

>>>>

```{julia}
using Dates
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using SpacePhysicsMakie: tplot
import SpaceDataModel
using SpaceDataModel: setmeta, times
using TimeseriesUtilities
using Speasy
using GLMakie
using DataFrames, DimensionalData
```

@@

```{julia}
tmin = DateTime("2021-01-15")
tvars = [
    spz"cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN, VEL_SC, VEL_INST, MAGF_SC"...,
    spz"PSP_FLD_L2_MAG_SC_4_SA_PER_CYC/psp_fld_l2_mag_SC_4_Sa_per_Cyc"
]
tplot(tvars, tmin, tmin + Hour(1))
```

@@

```{julia}
using Discontinuity

tmin = DateTime("2021-01-15")

# Get results from both methods
function get_discontinuity_results(tmin, tmax, B, V)
    @info resolution(B)
    @info resolution(V)
    df_pvi = Discontinuity.ids_finder_PVI(B, V; every=Hour(2))
    df_cvi = Discontinuity.ids_finder_CVI(B, V; every=Hour(2), std_threshold=2)
    df_variance = Discontinuity.ids_finder(B, V; tau=Second(2))
    CVI_ts = CVI(B)
    PVI_ts = PVI(B)
    return (; df_pvi, df_cvi, df_variance, CVI_ts, PVI_ts)
end

function get_discontinuity_results(tmin, tmax, B_prod::Product, V_prod::Product)
    B = DimArray(B_prod(tmin, tmax))
    V = DimArray(V_prod(tmin, tmax))
    return get_discontinuity_results(tmin, tmax, B, V)
end

psp_results = get_discontinuity_results(tmin, tmin + Day(1), PSP.B, PSP.V)
wind_results = get_discontinuity_results(tmin, tmin + Day(1), Wind.B_GSE, Wind.V_GSE_3DP)

# info the number of events
@info "Number of events for PSP" nrow.(getproperty.(Ref(psp_results), (:df_pvi, :df_cvi, :df_variance)))
@info "Number of events for Wind" nrow.(getproperty.(Ref(wind_results), (:df_pvi, :df_cvi, :df_variance)))
```

Test if the CVI and PVI could capture the discontinuities

```{julia}
t0 = DateTime("2021-01-15T09:11")
t1 = DateTime("2021-01-15T09:14")
B_subset = tview(B, t0, t1)
V_subset = tview(V, t0, t1)
df_pvi = Discontinuity.ids_finder_PVI(B_subset, V_subset)
df_cvi = Discontinuity.ids_finder_CVI(B_subset, V_subset)
df_variance = Discontinuity.ids_finder(B_subset; tau=Second(30))

CVI_ts = CVI(B_subset)
PVI_ts = PVI(B_subset)

f = Figure(size=(1400, 1000))

tplot(f[1, 1], [B_subset, [CVI_ts, PVI_ts]])

# Plot 3 candidates from PVI method
for i in 1:min(3, nrow(df_pvi))
    plot_candidate(f[2, 1][i, 1], df_pvi[i, :], [PSP.B,])
end
for i in 1:min(3, nrow(df_cvi))
    plot_candidate(f[2, 2][i, 1], df_cvi[i, :], [PSP.B,])
end
for i in 1:min(3, nrow(df_variance))
    plot_candidate(f[2, 3][i, 1], df_variance[i, :], [PSP.B,])
end
f

```

```{julia}
using Random

f = Figure(size=(1400, 1000))
# Plot 3 candidates from PVI method
for i in 1:min(3, nrow(df_pvi))
    plot_candidate(f[i, 1], df_pvi[i, :], [PSP.B, [CVI_ts, PVI_ts]])
end
random_indices = randperm(nrow(df_cvi))[1:min(3, nrow(df_cvi))]
for (plot_idx, i) in enumerate(random_indices)
    plot_candidate(f[plot_idx, 2], df_cvi[i, :], [PSP.B, [CVI_ts, PVI_ts]])
end
random_indices = randperm(nrow(df_variance))[1:min(3, nrow(df_variance))]
for (plot_idx, i) in enumerate(random_indices)
    plot_candidate(f[plot_idx, 3], df_variance[i, :], [PSP.B, [CVI_ts, PVI_ts]])
end

# Add method labels on the left
Label(f[0, 1], "PVI\nMethod", fontsize=14, tellwidth=false)
Label(f[0, 2], "CVI\nMethod", fontsize=14, tellwidth=false)
Label(f[0, 3], "Variance\nMethod", fontsize=14, tellwidth=false)
resize_to_layout!()
f
```

#### The effect of n / τ on the detection

```{julia}
n_events = 6
n = 16
figsize = (n_events * 300, 400)
f = Figure(; size=figsize)
df = Discontinuity.ids_finder_CVI(B, V; std_threshold=2, n=n)
CVI_tmp = CVI(B; n=n)
# rows = rand(eachrow(df), n_events)

# sort by duration
df = sort(dropmissing(df), :duration; rev=true)
rows = eachrow(df)[1:n_events]
@info rows.duration
for (i, row) in enumerate(rows)
    @info getindex.(Ref(row), (:I_max, :index_std, :index_stability, :index_consistency))
    plot_candidate(f[1, i], row, [PSP.B, CVI_tmp])
end
resize_to_layout!()
f
```

```{julia}
n_events = 6
n = 16
figsize = (n_events * 300, 400)
f = Figure(; size=figsize)
df = Discontinuity.ids_finder(B, V; std_threshold=2, tau=Second(n))

# sort by duration
df = sort(dropmissing(df), :duration; rev=true)
rows = eachrow(df)[1:n_events]
@info rows.duration
for (i, row) in enumerate(rows)
    @info getindex.(Ref(row), (:index_std))
    plot_candidate(f[1, i], row, PSP.B)
end
resize_to_layout!()
f
```

```{julia}
f = Figure(size=(1400, 1000))

for (i, n) in enumerate([1, 2, 4, 32])
    df_cvi = Discontinuity.ids_finder_CVI(B, V; std_threshold=2, n=n)
    CVI_tmp = CVI(B; n=n)
    row = rand(eachrow(df_cvi))
    @info getindex.(Ref(row), (:I_max, :index_std, :index_stability, :index_consistency))
    plot_candidate(f[1, i], row, [PSP.B, CVI_tmp])
    f
end
f
```

```{julia}
f = Figure(size=(1400, 1000))

for (i, n) in enumerate([2, 4, 8, 32])
    df = Discontinuity.ids_finder(B, V; std_threshold=2, tau=Second(n))
    row = rand(eachrow(df))
    @info getindex.(Ref(row), (:index_std, :index_stability))
    plot_candidate(f[1, i], row, [PSP.B])
    f
end
f
```

### 2025-08-27 notebooks/00_index.qmd
refactor: clean a bit

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, compute_Alfvenicity_params!, filter_low_mva_quality
using SPEDAS
using DataFrames, DataFramesMeta
using GLMakie
using SPEDAS: set_meta, set_meta!
using Beforerr: _theme_legend, easy_save
using PartialFunctions

@@

```{julia}
using StatsBase
using DimensionalData
using NaNStatistics

function get_vl_ratio_ts(df, col, dt::TimePeriod=Hour(4))
    data = getproperty(df, col)
    vl_ratio_ts = DimArray(data, Ti(df.time))
    gfunc = x -> floor(x, dt)
    gdf = groupby(vl_ratio_ts, Ti => gfunc)
    vl_ratio_ts_m = nanmedian.(disallowmissing.(filter.(!ismissing, gdf)))
    n = rebuild(length.(gdf); metadata=(; ylabel="N (#)", plottype=:Stairs))
    set_meta!(vl_ratio_ts_m; ylabel=L"R_{VB}", labels=["Isotropy", "Anisotropy"], plottype=:Stairs)
    return vl_ratio_ts_m, n
end

function get_vl_ratio_ts(df, dt::TimePeriod=Hour(4))
    v_l_ratio_ts, n1 = get_vl_ratio_ts(df, :V_l_ratio, dt)
    v_l_ratio_Λ_ts, n2 = get_vl_ratio_ts(df, :V_l_ratio_Λ, dt)
    vl_ratio_ts = hcat(v_l_ratio_ts, v_l_ratio_Λ_ts)
    return vl_ratio_ts, n1
end
```

@@

```{julia}
function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
    tmin, tmax = t_us_ds(event)
    f = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
    tlines!(f, [tmin, tmax])
    f
end

f = let
    f = Figure(; size=(1200, 800))
    # plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)

@@

```{julia}
psp_df_taus = map([2, 4, 8, 16, 32]) do tau
    psp_config["tau"] = tau
    df = PSPAnisotropy.produce(psp_config)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end

wind_df_taus = map([2, 4, 8, 16, 32]) do tau
    wind_config["tau"] = tau
    df = PSPAnisotropy.produce(wind_config)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end
```

>>>>

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, compute_Alfvenicity_params!, filter_low_mva_quality
using SPEDAS
using DataFrames, DataFramesMeta
using GLMakie
using SPEDAS: setmeta, setmeta!
using Beforerr: _theme_legend, easy_save
using PartialFunctions

@@

@@

```{julia}
f = let
    f = Figure(; size=(1200, 800))
    # plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)

@@

```{julia}
psp_df_taus = map([2, 4, 8, 16, 32]) do tau
    psp_config["tau"] = tau
    df = PSPAnisotropy.produce(psp_config, psp_config["timeranges"][1]...)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end

wind_df_taus = map([2, 4, 8, 16, 32]) do tau
    wind_config["tau"] = tau
    df = PSPAnisotropy.produce(wind_config, wind_config["timeranges"][1]...)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end
```
